### 2020-04-20 final_report/methodology.tex
fix typo

To prevent undesirable bias in results due to training set selection, all metrics
collected in the scheme of $k$-fold cross-validation with a standard choice of
$k=5$. Herein, a sample set is subdivided into 5 disjoint folds which are
repeatedly interpreted as training and testing sets, maintaining a constant
ratio of samples between the two. In each such interpretation experiments are
repeated, and the overall value of each metric of interest is reported as the
mean across all folds.

@@

>>>>

To prevent undesirable bias in results due to training set selection, all metrics
are collected in the scheme of $k$-fold cross-validation with a standard choice of
$k=5$. Herein, a sample set is subdivided into 5 disjoint folds which are
repeatedly interpreted as training and testing sets, maintaining a constant
ratio of samples between the two. In each such interpretation experiments are
repeated, and the overall value of each metric of interest is reported as the
mean across all folds.

@@

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.20\textwidth}
		\centering
		{\footnotesize \incfigscale{0.62}{1h3f}}
		\caption{$\text{1h3f}(W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.15\textwidth}
		\centering
		{\footnotesize \incfigscale{0.62}{kf}}
		\caption{$\text{df}(D,W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.15\textwidth}
		\centering
		{\footnotesize \incfigscale{0.62}{3pyramid}}
		\caption{$\text{3pyr}(W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.20\textwidth}
		\centering
		{\footnotesize \incfigscale{0.62}{5diam}}
		\caption{$\text{5diam}(W)$}
	\end{subfigure}\hfill%
	\begin{subfigure}[b]{0.20\textwidth}
		\centering
		{\footnotesize \incfigscale{0.62}{kf}} % TODO
		\caption{$\text{6sym}(W)$}
	\end{subfigure}

	\caption{TODO}
	\label{fig:neural-net-architectures}
\end{figure}
